Clustering SCPCL000822 and SCPCL000824

### 2024-08-02 analyses/cell-type-ewings/exploratory_analysis/05-cluster-exploration.Rmd
Apply suggestions from code review
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

```{r, cluster_stats_functions}
# cluster statistics functions
# get silhouette width and cluster purity for each cluster
# calculates values across all nn_param options used to determine clustering
# all_cluster_results must have nn_param column
get_cluster_stats <- function(sce,
                              id,
                              all_cluster_results) {
  pcs <- reducedDim(sce, "PCA")

@@

# get cluster stability for each nn_param cluster results are available for
# calculated the ari between original clusters and shuffled clusters 20 times
get_cluster_stability <- function(sce,
                                  id,
                                  all_cluster_results) {
  pcs <- reducedDim(sce, "PCA")

@@

# plot stability across all values of k
ggplot(stability_df, aes(x = k_value, y = ari)) +
  geom_point() +
  facet_grid(rows = vars(library_id)) +
  labs(title = "Cluster stability")
```

@@

From these plots, it's obvious that K = 5 is over clustering and cell types are spread across a lot of clusters. 
However, for the other values of K, there doesn't seem to be any striking difference that are obvious by eye.

@@

# create individual density plots and combine into one
marker_gene_columns |>
  purrr::map(\(column){
    genelist_name <- stringr::str_remove(column, "_sum")

>>>>

```{r, cluster_stats_functions}
# cluster statistics functions

# get silhouette width and cluster purity for each cluster
# calculates values across all nn_param options used to determine clustering
# all_cluster_results must have nn_param column
get_cluster_stats <- function(sce,
                              id,
                              all_cluster_results) {
  pcs <- reducedDim(sce, "PCA")

@@

# get cluster stability for each nn_param cluster results are available for
get_cluster_stability <- function(sce,
                                  id,
                                  all_cluster_results) {
  pcs <- reducedDim(sce, "PCA")

@@

# plot stability across all values of k
ggplot(stability_df, aes(x = k_value, y = ari)) +
  geom_jitter(width = 0.1) +
  facet_grid(rows = vars(library_id)) +
  labs(title = "Cluster stability")
```

@@

From these plots, it's obvious that K = 5 is over clustering and cell types are spread across a lot of clusters. 
However, for the other values of K, there don't seem to be any striking differences that are obvious by eye.

@@

# create individual umaps and combine into one
marker_gene_columns |>
  purrr::map(\(column){
    genelist_name <- stringr::str_remove(column, "_sum")
